---
title: "TVMaze API Vignette"
author: "Baldeep Dhada, Dylan Longert, Somya Nagar"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TVMaze API Vignette}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Load tvmazeWrapper Package

```{r}
library(tvmazeWrapper)
```

### Using Fuctions

**get_shows():** An API call is made to the TVmaze database with the
television show the user inputed as a parameter. The function returns a
dataframe of all television shows similar to what the user inputed, as
well as all associated data found within the database. NULL is returned
if the television show is not found within the database.

**example:**

```{r}
shows <- get_shows("Game of Thrones")
head(shows, 1)
```

**format_show_name():** This function formats the dataframe returned in
the get_shows() function, returning only the television show name,
premier date, end date, and genres.

**example:**

```{r}
format_show_name(shows)
```

**get_seasons():** second API call is made to the TVmaze database with
television show id as a parameter. This function returns a dataframe of
all available data pertaining to a specific television show.

**example:**

```{r}
# 82 is the television show id parameter for Game of Thrones
seasons_df <- get_seasons(82)
head(seasons_df, 1)
```

**format_season_name():** This function formats the dataframe returned
in the get_seasons() function, returning only season numbers, season
names, premier dates, end dates, and number of episodes.

**example:**

```{r}
# seasons_df is the dataframe with seasons data
seasons <- format_season_name(seasons_df)
head(seasons)
```

**get_episodes_of_season():** A third API call is made to the TVMaze
database with season id as a parameter. This function returns a
dataframe of all available data pertaining to the season of a television
show.

```{r}
# 307 is the season id for season 1 of Game of Thrones
episodes_df <- get_episodes_of_season(307)
head(episodes_df, 1)
```

**format_episode_name():** This function formats the dataframe returned
in the get_episodes_of_season() function, returning only episode
numbers, episode names, and episode ratings.

```{r}
episodes <- format_episode_name(episodes_df)
head(episodes)
```

**get_all_episodes():** A fourth API call is made to the TVMaze database
with television show id as a parameter. This function returns a
dataframe of all available television show episode data.

```{r}
# 82 is the television show id parameter for Game of Thrones
all_episodes_df <- get_all_episodes(82)
head(all_episodes_df, 1)
```

**format_all_episodes():** This function formats the dataframe returned
in the get_all_episodes() function, returning only episode numbers,
episode names, and episode ratings.

```{r}
all_episodes <- format_all_episodes(all_episodes_df)
head(all_episodes)
```

**generate_ratings_plot():** This function utilizes the data generated
from the format_episode_name() function to produce a visualization of a
television shows average rating per season plotted over season.

```{r fig.width=8, fig.height=5}
generate_ratings_plot(all_episodes)
```

**generate_season_ratings_plot():** This function utilizes the data
generated from the format_all_episodes() function to produce a
visualization of a television shows average rating per episode plotted
over episode.

```{r fig.width=8, fig.height=5}
generate_season_ratings_plot(episodes)
```

All of the functionality explained above can be accessed with the
`main()` function. It allows the user with an interactive experience to
navigate the entire workflow. The usage for that demonstrated below :

**main() :**

``` R
main()

Enter a Show (or 0 to exit): Game of thrones

Select a Show Number (or 0 to exit): 1

Select a Season Number (or 0 to exit): 1

1. Plot of average rating per season for all the seasons in a show 
2. Plot of ratings for each episodes in a season
Do you want to see any of the 2 visualizations? (or 0 to exit): 1

Enter a Show (or 0 to exit): 0
```
